\chapter*{Introduction}

\section*{About the SMO}
The Singapore Mathematical Olympiad (SMO) is an annual mathematical competition organized by the Singapore Mathematical Society. The Olympiad is split into three categories, namely Junior, Senior and Open. Within each category, there are two rounds of papers (the second being an invitational round).

\section*{About the Compendium}

This compendium is written with the goal to provide clear and concise solutions to each and every problem that has appeared in the SMO. The compendium has been split into two parts: Problems and Solutions. Within each part, SMO papers are further categorized by year, category and round.

\section*{Other Resources}
Links to relevant resources, such as \href{https://www.youtube.com/c/WayTan}{\textit{Way Tan}}'s reviews of Round 1 papers, and \href{https://artofproblemsolving.com/}{\textit{Art of Problem Solving}} threads for Round 2 questions, are provided at the beginning of solutions. A less well-known but equally enriching resource for olympiad preparation is the \href{https://simoxmenblog.blogspot.com/}{\textit{SIMO Retiree Blog}}.

\section*{Contributing}

The source code for this compendium can be found on GitHub at \href{https://github.com/asdia0/Compendium}{\texttt{asdia0/Compendium}}. Contributions are more than welcome.

\section*{Acknowledgements}

Not all solutions presented in this compendium are original; credits will be displayed at the start of relevant solutions. The template for this compendium is adapted from Evan Chen's  \LaTeX\ style file \href{https://github.com/vEnhance/dotfiles/blob/main/texmf/tex/latex/evan/evan.sty}{\texttt{evan.sty}}.
